---
title: "SPOT-CHECK - C3 DASHBOARD"
output: 
  flexdashboard::flex_dashboard:
    orientation: row
    vertical_layout: fill
---

```{r setup, include=FALSE}

library(flexdashboard)
library(haven)
library(plyr)
library(tidyverse)
library(dplyr)
library(lubridate)
library(highcharter)
library(plotly)
library(DT)
library(stringr)
library(ggplot2)
library(viridis)
library(hrbrthemes)
library(scales)

```

```{r }
#Woreda data

woreda_data<-read_dta("C:/Survey Spotcheck II/Data/Raw_data/PSNP_WOREDA_FINAL_AMH_AFAR/PSNP_WOREDA_FINAL_AMH_AFAR.dta")
woreda_data <- as_factor(woreda_data) 
woreda_data <- droplevels(woreda_data)
#woreda_data <- droplevels(woreda_data) %>%  mutate(region = str_replace(region,"South West Ethiopia", "SW Ethiopia"))
#Id
woreda_id <-woreda_data %>% select(interview__key,region, woreda)



#Kebele data
kebele_data<-read_dta("C:/Survey Spotcheck II/Data/Raw_data/PSNP_5_KEBELE_FINAL_AMH_AFAR/PSNP_5_KEBELE_FINAL_AMH_AFAR.dta")
kebele_data <- as_factor(kebele_data) 
kebele_data <- droplevels(kebele_data)
#kebele_data <- droplevels(kebele_data) %>%  mutate(region = str_replace(region,"South West Ethiopia", "SW Ethiopia"))
#Id
kebele_id <-kebele_data %>% select(interview__key,region, woreda)


#Household data
hh_data<-read_dta("C:/Survey Spotcheck II/Data/Raw_data/PSNP_5_HOUSEHOLD_FINAL_AMH_AFAR/PSNP_5_HOUSEHOLD_FINAL_AMH_AFAR.dta")
hh_data <- as_factor(hh_data) 
hh_data <- droplevels(hh_data)
#hh_data <- droplevels(hh_data) %>%  mutate(region = str_replace(region,"South West Ethiopia", "SW Ethiopia"))

```


WOREDA
=====================================
row 
-------------------------------------
```{r}
# Woreda Offices
WFSD <- woreda_data %>% filter(woreda_level__1==1 ) %>% nrow()
WEWRD<-woreda_data %>% filter(woreda_level__2==1 ) %>% nrow()
WNRD <-woreda_data %>% filter(woreda_level__3==1 ) %>% nrow()
WLS  <-woreda_data %>% filter(woreda_level__4==1 ) %>% nrow()
WOLSA<-woreda_data %>% filter(woreda_level__5==1 ) %>% nrow()
WCPO <-woreda_data %>% filter(woreda_level__6==1 ) %>% nrow()
WOFED<-woreda_data %>% filter(woreda_level__7==1 ) %>% nrow()
FDP  <-woreda_data %>% filter(woreda_level__8==1 ) %>% nrow()
WEPSC<-woreda_data %>% filter(woreda_level__9==1 ) %>% nrow()
WGHO<-woreda_data %>% filter(woreda_level__10==1 ) %>% nrow()
```


### WFSD

```{r}

valueBox(WFSD)
```

### WEWRD

```{r}

valueBox(WEWRD)
```

### WNRD

```{r}

valueBox(WNRD)
```

### WLS

```{r}

valueBox(WLS)
```

### WOLSA

```{r}

valueBox(WOLSA)
```


### WCPO

```{r}

valueBox(WCPO)
```

### WOFED

```{r}

valueBox(WOFED)
```

### FDP

```{r}

valueBox(FDP)
```

### WEPSC

```{r}

valueBox(WEPSC)
```

### WGHO

```{r}

valueBox(WGHO)
```



column 
-------------------------------------

### **Available Documents** {data-width=500}

```{r}

doc_p1<-read_dta("C:/Survey Spotcheck II/Data/Raw_data/PSNP_WOREDA_FINAL_AMH_AFAR/documents_1.dta")
doc_p1 <- as_factor(doc_p1) 
doc_p1 <- droplevels(doc_p1)

doc_p1 <- inner_join(x = doc_p1, y = woreda_id, by="interview__key")

p1_doc <- doc_p1 %>% select(interview__key, documents_1__id, region, woreda, P1_C1) %>% drop_na() %>% 
   mutate(documents_1__id = str_replace(documents_1__id,"PSNP GSD and Nutrition mainstreaming facilitators manual", "PSNP GSD & Nutr."), documents_1__id = str_replace(documents_1__id,"PSNP Financial Management Manual", "PSNP Fin. mgt"), documents_1__id = str_replace(documents_1__id, "BCC facilitation guide/manua", "BCC fac"), documents_1__id = str_replace(documents_1__id, "Livelihood transfer guidance note", "Livelihood trans."), documents_1__id = str_replace(documents_1__id, "Voluntary loss of asset format", "Voluntary"), documents_1__id = str_replace(documents_1__id, "Specifications and work norms", "Sp.&work norm"), documents_1__id = str_replace(documents_1__id, "ESMF Screening format", "ESMF Screening"), documents_1__id = str_replace(documents_1__id, "Contingency Planning Guidelines", "Contingency Plan"),documents_1__id = str_replace(documents_1__id, "ESMF Operational Summary", "ESMF Operational"), documents_1__id = str_replace(documents_1__id, "ESMF Operational Summary", "ESMF Operational")) %>% 
  filter(P1_C1=="Yes") %>% group_by(documents_1__id) %>% summarise(count=n())


  
  
d1<-p1_doc %>% 
  plot_ly(x=~count, 
          y=~documents_1__id, 
          color=~documents_1__id,
          colors="Set1",
          text=~count,
          showlegend = F,
          textposition="outside",
          hovertext = ~paste("Document=", documents_1__id, "<br>", "Available doc=", count, "<br>"), 
          hoverinfo = "text") %>% 
  add_bars() %>% 
  layout(title="",
         xaxis = list(title="n",  showgrid = F),
         yaxis = list(title = "",categoryorder = "total ascending",  showgrid = F),
         barmode="group")


d1 <- plotly::config(d1, displayModeBar = FALSE)

d1

```

### **Re-targeting Conducted** {data-width=350}
```{r}

colors42=c('#FFD93D', '#7AA874')

w_retargeting <- woreda_data %>%
  select(region, P1_D15) %>% 
  drop_na() %>% 
  group_by(region,P1_D15) %>%
  count(name="n_answers") %>% 
  group_by(region) %>% 
  mutate(percent_answers = n_answers / sum(n_answers)) %>% 
  mutate(percent_answers_label = percent(percent_answers, accuracy = 1)) 

p_w_retargeting<-w_retargeting %>% 
  plot_ly(x=~region, 
          y=~n_answers, 
          color=~P1_D15,
          colors=colors42,
          text=~percent_answers_label,
          #showlegend = F,
          textposition="outside",
          hovertext = ~paste("n=", n_answers, "<br>", "Percent=",percent_answers_label, "<br>"), 
          hoverinfo = "text") %>% 

  add_bars() %>% 
  layout(title="",
         xaxis = list(title="", categoryorder = "total descending", showgrid = F),
         yaxis = list(title = "n", showgrid = F),
         barmode="group")


p_w_retargeting <- plotly::config(p_w_retargeting, displayModeBar = FALSE)

p_w_retargeting
```

 

### **Avg no. of Technical Staff by woreda** {data-width=300}  
```{r }
colors6=c('#009FBD', '#FFD93D', '#FF6000')
No_tech_staff<-woreda_data %>% 
  group_by(woreda) %>% 
  summarise(No_of_staff = sum(P1_B20))%>% 
  drop_na() 

# avg_tech_staff_reg<-avg_tech_staff %>% 
#   group_by(woreda) %>%
#   summarise(avg_tech_staff = count(Average_staff)) %>% 
#   mutate(across(where(is.numeric), round, 0))

p_no_tech_staff <-No_tech_staff %>% 
  plot_ly(x=~woreda, 
          y=~No_of_staff, 
          color=~woreda,
          colors=colors6,
          text=~No_of_staff,
          textposition="outside",
          hovertext = ~paste("Woreda=", woreda, "<br>", "No. technical staff=", No_of_staff, "<br>"), 
          hoverinfo = "text") %>% 
  add_bars() %>% 
  layout(title="",
         xaxis = list(title=""),
         yaxis = list(title = "n"),
         barmode="group")
p_no_tech_staff <- plotly::config(p_no_tech_staff, displayModeBar = FALSE)
p_no_tech_staff
```



column 
-------------------------------------


### **Document Maintained** {data-width=400}
```{r}
colors4=c('#1F8A70','#30E3DF','#497174','#FF6000', '#FFD93D', '#7AA874', '#009FBD')
record_k1<-read_dta("C:/Survey Spotcheck II/Data/Raw_data/PSNP_WOREDA_FINAL_AMH_AFAR/Record_Keeping_1.dta")
record_k1 <- as_factor(record_k1) 
record_k1 <- droplevels(record_k1)
options(digits=1) 

record_k1 <- inner_join(x = record_k1, y = woreda_id, by="interview__key")

p1_record <- record_k1 %>%
  select(region, Record_Keeping_1__id, woreda, P1_B21, P1_B21_1) %>% 
  mutate(Record_Keeping_1__id = str_replace(Record_Keeping_1__id,"PDS monthly payroll", "PDS payroll"), Record_Keeping_1__id = str_replace(Record_Keeping_1__id,"PW attendance sheet", "PW attendance")) %>% 
  filter(P1_B21=="Yes saw the document") %>% 
  group_by(woreda, Record_Keeping_1__id) %>%
  count(name="n_answers") %>% 
  #group_by(region) %>% 
  mutate(percent_answers = n_answers / sum(n_answers)) %>% 
  mutate(percent_answers_label = percent(percent_answers, accuracy = 1)) 
  

p5<-p1_record %>% 
  plot_ly(x=~woreda, 
          y=~n_answers, 
          color=~Record_Keeping_1__id,
          colors=colors4,
          text=~n_answers,
          #showlegend = F,
          #textposition="outside",
          hovertext = ~paste("n=", n_answers, "<br>", "Percent=",percent_answers_label, "<br>"), 
          hoverinfo = "text") %>% 

  add_bars() %>% 
  layout(title="",
         xaxis = list(title="", categoryorder = "total descending", showgrid = F),
         yaxis = list(title = "n", showgrid = F),
         barmode="stack")


p5 <- plotly::config(p5, displayModeBar = FALSE)

p5
```


### **Forms Record Maintained by** {data-width=400}
```{r}
colors55=c('#FFD93D','#FF6000', '#009FBD', '#30E3DF')
record_k2<-read_dta("C:/Survey Spotcheck II/Data/Raw_data/PSNP_WOREDA_FINAL_AMH_AFAR/Record_Keeping_1.dta")
record_k2 <- as_factor(record_k2) 
record_k2 <- droplevels(record_k2)
options(digits=1) 

record_k2 <- inner_join(x = record_k2, y = woreda_id, by="interview__key")

p2_record <- record_k2 %>%
  select(woreda, Record_Keeping_1__id, P1_B21, P1_B21_1) %>% drop_na() %>% 
  mutate(Record_Keeping_1__id = str_replace(Record_Keeping_1__id,"PDS monthly payroll", "PDS payroll"), Record_Keeping_1__id = str_replace(Record_Keeping_1__id,"PW attendance sheet", "PW attendance")) %>% 
  #drop_na() %>% 
  group_by(woreda,P1_B21_1) %>%
  count(name="n_answers2") %>% 
  group_by(woreda) %>% 
  mutate(percent_answers2 = n_answers2 / sum(n_answers2)) %>% 
  mutate(percent_answers_label2 = percent(percent_answers2, accuracy = 1)) 
  


p6<-p2_record %>% 
  plot_ly(x=~woreda, 
          y=~n_answers2, 
          color=~P1_B21_1,
          colors=colors55,
          text=~percent_answers_label2,
          #showlegend = F,
          textposition="outside",
          hovertext = ~paste("n=", n_answers2, "<br>", "Percent=",percent_answers_label2, "<br>"), 
          hoverinfo = "text") %>% 

  add_bars() %>% 
  layout(title="",
         xaxis = list(title="", categoryorder = "total descending", showgrid = F),
         yaxis = list(title = "n", showgrid = F),
         barmode="group")


p6 <- plotly::config(p6, displayModeBar = FALSE)

p6
```


### **Appeal cases has the WFSD received in 2015 EFY** {data-width=400}
```{r}

appeal<-woreda_data %>% select(woreda,P1_F5) %>%drop_na() %>% 
  group_by(woreda) %>% summarise(n_answer=sum(P1_F5))
  
colors=c('#F99417','#5D3891','#89375F','#CE5959')

p_appeal <- plot_ly(appeal, labels = ~woreda, values = ~n_answer, type = 'pie', marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))
p_appeal <- p_appeal %>% layout(title = '',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

p_appeal
```



KEBELE
=====================================
row 
-------------------------------------

```{r}
KFSTF<- kebele_data %>% filter(k_institution__1==1 ) %>% nrow()
CFSTF<-kebele_data %>% filter(k_institution__2==1 ) %>% nrow()
DA<-kebele_data %>% filter(k_institution__3==1 ) %>% nrow()
KAC<-kebele_data %>% filter(k_institution__4==1 ) %>% nrow()
PW_pc<-kebele_data %>% filter(k_institution__5==1 ) %>% nrow()
CFs <-kebele_data %>% filter(k_institution__6==1 ) %>% nrow()

TOTAL <- kebele_data%>% nrow()
```




### KFSTF

```{r}

valueBox(KFSTF)
```

### CFSTF

```{r}

valueBox(CFSTF)
```

### DA

```{r}

valueBox(DA)
```

### KAC

```{r}

valueBox(KAC)
```


### PW pc

```{r}

valueBox(PW_pc)
```


### CFs

```{r}

valueBox(CFs)
```

### TOTAL

```{r}

valueBox(TOTAL,icon = "fa-clock", color = "#FF6000")
```

column 
-------------------------------------



```{r}

# #kebeles Tool Type
# kebele_tools <- c("KFSTF","CFSTF","DA","KAC","PW cp","CFs")
# kebele_tools_no <-c(KFSTF,CFSTF,DA,KAC,PW_pc,CFs)
# 
# kebele_inst <- data.frame(kebele_tools, kebele_tools_no)
# kebele_inst <- kebele_inst %>% arrange(kebele_tools_no)
# kebele_inst$kebele_tools<- factor(kebele_inst$kebele_tools, levels=kebele_inst[["kebele_tools"]])
# 
# 
# #plot fig
# P_keb_tool <- kebele_inst %>% plot_ly()
# P_keb_tool <- P_keb_tool %>% add_trace(x = ~kebele_tools, y = ~kebele_tools_no, type = 'bar',  name = 'Kebele Institut', marker = list(color = '#5D3891'))
# 
# P_keb_tool <- P_keb_tool %>% layout(xaxis = list(title = ''), barmode = 'group')          
# P_keb_tool <- P_keb_tool %>% layout(yaxis = list(title = 'n'), barmode = 'group')
# 
# P_keb_tool 
```


### **Document Availability** {data-width=300}

```{r }
k_doc1<-read_dta("C:/Survey Spotcheck II/Data/Raw_data/PSNP_5_KEBELE_FINAL_AMH_AFAR/PSNP_available_doc.dta")
k_doc1 <- as_factor(k_doc1) 
k_doc1 <- droplevels(k_doc1)

k_doc1 <- inner_join(x = k_doc1, y = kebele_id, by="interview__key")

k_doc_aval <- k_doc1 %>% select(interview__key, PSNP_available_doc__id, region, woreda, Q19) %>% drop_na() %>% 
  # mutate(documents_1__id = str_replace(documents_1__id,"PSNP GSD and Nutrition mainstreaming facilitators manual", "PSNP GSD & Nutr."), documents_1__id = str_replace(documents_1__id,"PSNP Financial Management Manual", "PSNP Fin. mgt"), documents_1__id = str_replace(documents_1__id, "BCC facilitation guide/manua", "BCC fac"), documents_1__id = str_replace(documents_1__id, "Livelihood transfer guidance note", "Livelihood trans."), documents_1__id = str_replace(documents_1__id, "Voluntary loss of asset format", "Voluntary"), documents_1__id = str_replace(documents_1__id, "Specifications and work norms", "Sp.&work norm"), documents_1__id = str_replace(documents_1__id, "ESMF Screening format", "ESMF Screening"), documents_1__id = str_replace(documents_1__id, "Contingency Planning Guidelines", "Contingency Plan"),documents_1__id = str_replace(documents_1__id, "ESMF Operational Summary", "ESMF Operational"), documents_1__id = str_replace(documents_1__id, "ESMF Operational Summary", "ESMF Operational")) %>% 
  filter(Q19=="Yes, I saw the document") %>% group_by(PSNP_available_doc__id) %>% summarise(count=n())
  
  
p_doc_aval<-k_doc_aval %>% 
  plot_ly(y=~PSNP_available_doc__id, 
          x=~count, 
          color=~PSNP_available_doc__id,
          colors="Set1",
          text=~count,
          showlegend = F,
          textposition="outside",
          hovertext = ~paste("Document=", PSNP_available_doc__id, "<br>", "Available doc=", count, "<br>"), 
          hoverinfo = "text") %>% 
  add_bars() %>% 
  layout(title="",
         xaxis = list(title="n", showgrid = F),
         yaxis = list(title = "",  categoryorder = "total ascending", showgrid = F),
         barmode="group")


p_doc_aval <- plotly::config(p_doc_aval, displayModeBar = FALSE)

p_doc_aval
```

### **Appeal cases has the KAC received in 2015 EFY** {data-width=300}
```{r}
appeal_kac<- kebele_data %>% select(woreda,D4_Q2) %>%drop_na() %>% 
  group_by(woreda) %>% summarise(n_answer=sum(D4_Q2))
  
colors=c('#F99417','#5D3891','#89375F','#CE5959')

p_appeal_kac <- plot_ly(appeal_kac, labels = ~woreda, values = ~n_answer, type = 'pie', marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))
p_appeal_kac <- p_appeal_kac %>% layout(title = '',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

p_appeal_kac 

```

### **Document Maintained** {data-width=300}
```{r}
colors52=c('#30E3DF', '#009FBD','#FF6000', '#FFD93D', '#7AA874')

record_k2<-read_dta("C:/Survey Spotcheck II/Data/Raw_data/PSNP_5_KEBELE_FINAL_AMH_AFAR/records.dta")
record_k2 <- as_factor(record_k2) 
record_k2 <- droplevels(record_k2)
options(digits=1) 

record_k2 <- inner_join(x = record_k2, y = kebele_id, by="interview__key")

p_record2 <- record_k2 %>%
  select(region, records__id, woreda, B3_Q13) %>% 
  filter(B3_Q13=="Yes saw the document") %>% 
  group_by(woreda, records__id) %>%
  count(name="n_answers") %>% 
  group_by(woreda) %>% 
  mutate(percent_answers = n_answers / sum(n_answers)) %>% 
  mutate(percent_answers_label = percent(percent_answers, accuracy = 1)) 
  

p52<-p_record2 %>% 
  plot_ly(x=~woreda, 
          y=~n_answers, 
          color=~records__id,
          colors=colors52,
          text=~n_answers,
          #showlegend = F,
          #textposition="outside",
          hovertext = ~paste("n=", n_answers, "<br>", "Percent=",percent_answers_label, "<br>"), 
          hoverinfo = "text") %>% 

  add_bars() %>% 
  layout(title="",
         xaxis = list(title="", categoryorder = "total descending", showgrid = F),
         yaxis = list(title = "n", showgrid = F),
         barmode="stack")


p52 <- plotly::config(p52, displayModeBar = FALSE)

p52
```

column 
-------------------------------------

### **Average days of PW per week** {data-width=300}
```{r }
colors7=c('#009FBD','#FF6000', '#FFD93D', '#7AA874')
pw_day_per_week<-kebele_data %>% 
  group_by(woreda, interview__key) %>% 
  summarise(Average_day = mean(E1_Q7))%>% 
  drop_na() 

avg_day_per_week_reg<-pw_day_per_week %>% 
  group_by(woreda) %>%
  summarise(avg_day_per_week = mean(Average_day)) %>% 
  mutate(across(where(is.numeric), round, 2))

p_day_per_week <-avg_day_per_week_reg %>% 
  plot_ly(x=~woreda, 
          y=~avg_day_per_week, 
          color=~woreda,
          colors=colors7,
          text=~avg_day_per_week,
          textposition="outside",
          hovertext = ~paste("Woreda=", woreda, "<br>", "Avg PW days=", avg_day_per_week, "<br>"), 
          hoverinfo = "text") %>% 
  add_bars() %>% 
  layout(title="",
         xaxis = list(title="", categoryorder = "total descending"),
         yaxis = list(title = "days"),
         barmode="group")
p_day_per_week <- plotly::config(p_day_per_week, displayModeBar = FALSE)
p_day_per_week
```



### **Average hours of PW per week** {data-width=300}
```{r }
colors6=c('#009FBD','#FF6000', '#FFD93D', '#7AA874')
pw_hr_per_week<-kebele_data %>% 
  group_by(woreda, interview__key) %>% 
  summarise(Average_hr = mean(E1_Q8))%>% 
  drop_na() 

avg_hr_per_week_reg<-pw_hr_per_week %>% 
  group_by(woreda) %>%
  summarise(avg_hr_per_week = mean(Average_hr)) %>% 
  mutate(across(where(is.numeric), round, 0))

p_hr_per_week <-avg_hr_per_week_reg %>% 
  plot_ly(x=~woreda, 
          y=~avg_hr_per_week, 
          color=~woreda,
          colors=colors6,
          text=~avg_hr_per_week,
          textposition="outside",
          hovertext = ~paste("Woreda=", woreda, "<br>", "Avg. PW hour=", avg_hr_per_week, "<br>"), 
          hoverinfo = "text") %>% 
  add_bars() %>% 
  layout(title="",
         xaxis = list(title=""),
         yaxis = list(title = "hours"),
         barmode="group")
p_hr_per_week <- plotly::config(p_hr_per_week, displayModeBar = FALSE)
p_hr_per_week
```

### **Project Implementation** {data-width=400}
```{r}
projects<-kebele_data %>% select(region, woreda, Tot_Planned_Subprojs_III,Tot_Impl_Subprojs_III) %>% 
  group_by(region, woreda) %>% 
  mutate(Impl_proj=sum(Tot_Impl_Subprojs_III), Plan_proj=sum(Tot_Planned_Subprojs_III))  

proj_reg<-projects %>% select(woreda,Impl_proj, Plan_proj) %>% 
  group_by(woreda) %>% summarise(impl=sum(Impl_proj), plan=sum(Plan_proj))


p_proj <- proj_reg %>% plot_ly()
p_proj <- p_proj %>% add_trace(x = ~woreda, y = ~impl, type = 'bar',  name = 'Implmented', marker = list(color = '#FF6000'))
p_proj <- p_proj %>% add_trace(x = ~woreda, y = ~plan, type = 'bar', name = 'Planned', marker = list(color = '#009FBD'))
p_proj <- p_proj %>% layout(xaxis = list(title = ''), barmode = 'group')          
p_proj <- p_proj %>% layout(yaxis = list(title = 'n'), barmode = 'group')
p_proj <- p_proj %>% layout(legend = list(x = 0, y = 1, orientation = 'h'))

p_proj
```

HOUSEHOLD
=====================================

row 
-------------------------------------
```{r}
# HH type
options(digits=1)
PWS <- hh_data %>% filter(Id_8__1==1) %>% nrow()
PDS<-hh_data %>% filter(Id_8__2==1) %>% nrow()
SR <-hh_data %>% filter(Id_8__3==1) %>% nrow()
LH  <-hh_data %>% filter(Id_8__4==1) %>% nrow()
TDS<-hh_data %>% filter(Id_8__5==1) %>% nrow()

Total_Synced <-hh_data %>% nrow()

```


### PWS

```{r}

valueBox(PWS, icon = "fa-bar-chart")
```

### PDS

```{r}

valueBox(PDS, icon = "fa-bar-chart")
```

### TDS

```{r}

valueBox(TDS, icon = "fa-bar-chart")
```

### LH

```{r}

valueBox(LH, icon = "fa-bar-chart")
```

### SR

```{r}

valueBox(SR, icon = "fa-bar-chart")
```

### TOTAL

```{r}

valueBox(Total_Synced,icon = "fa-clock", color = "#FF6000")
```



column 
-------------------------------------

### **Household Category**


```{r}


#Household tool
hh_type <- c("PWS","PDS","SR",	"LH","TDS")
hh_type_no <-c(PWS, PDS,	SR,	LH,	TDS)

household_types <- data.frame(hh_type, hh_type_no)
household_types <- household_types %>% arrange(hh_type_no)
household_types$hh_type<- factor(household_types$hh_type, levels=household_types[["hh_type"]])



#plot fig
fig1 <- household_types %>% plot_ly()
fig1 <- fig1 %>% add_trace(x = ~hh_type, y = ~hh_type_no, type = 'bar',  name = 'Household type', marker = list(color = '#006E7F'))

fig1 <- fig1 %>% layout(xaxis = list(title = ''), barmode = 'group')          
fig1 <- fig1 %>% layout(yaxis = list(title = 'n'), barmode = 'group')

fig1
```



### **Information received about targeting criteria** 
```{r}
colors9=c('#009FBD','#FF6000', '#FFD93D', '#7AA874')
targeting<- hh_data %>% 
  
  group_by(woreda, S4_Q2) %>%
  count(name="n_answers") %>%
  group_by(woreda) %>% 
  mutate(percent_answers = n_answers / sum(n_answers)) %>% 
  #mutate(across(where(is.numeric), round, 0)) %>% 
  mutate(percent_answers_label = percent(percent_answers, accuracy = 1)) %>%
  
  #filter(S4_Q2=="Yes") %>% 
  
   plot_ly(x=~woreda, 
          y=~n_answers, 
          text=~percent_answers_label,
          textposition="outside",
          colors=colors9,
          color=~S4_Q2,
          hovertext = ~paste("Woreda=", woreda, "<br>", "Percent=", percent_answers_label, "<br>", "n=",n_answers), 
          hoverinfo = "text") %>% 
         
  add_bars() %>% 
  layout(title="",
         xaxis = list(title="", categoryorder = "total descending"),
         yaxis = list(title = "n"),
         barmode="group")

targeting <- plotly::config(targeting, displayModeBar = FALSE)
targeting
```

### **Satisfaction in re-targeting**

```{r }
colors3=c('#009FBD','#FF6000', '#FFD93D', '#7AA874')
 re_targeting<-hh_data %>%  
  mutate(S4_Q13 = str_replace(S4_Q13,"Neither satisfied/Nor dissatisfied", "Neither")) %>% 
  group_by(woreda, S4_Q13) %>%
  count(name="n_answers") %>%
  drop_na() %>% 
  group_by(woreda) %>% 
  mutate(percent_answers = (n_answers / sum(n_answers))) %>% 
  #mutate(across(where(is.numeric), round, 0)) %>% 
  mutate(percent_answers_label = percent(percent_answers, accuracy = 1)) %>%
  
  plot_ly(x=~woreda, 
          y=~n_answers, 
          text=~percent_answers_label,
          textposition="outside",
          color=~S4_Q13,
          colors=colors3,
          hovertext = ~paste("re-targeting=", S4_Q13, "<br>", "Percent=", percent_answers_label, "<br>", "n=",n_answers), 
          hoverinfo = "text") %>% 
           
  add_bars() %>% 
  layout(title="",
         xaxis = list(title="", categoryorder = "total descending"),
         yaxis = list(title = "n"),
         barmode="group")
re_targeting <- plotly::config(re_targeting, displayModeBar = FALSE)
re_targeting
```


column 
-------------------------------------
### **Average household land size per woreda** 


```{r }
avg_hh_land<-hh_data %>% 
  group_by(woreda, interview__key) %>% 
  summarise(Average_land_size = mean(Q2))%>% 
  drop_na() 

avg_land_per_hh_reg<-avg_hh_land %>% 
  group_by(woreda) %>%
  summarise(avg_land_size_hh = mean(Average_land_size)) %>% 
  mutate(across(where(is.numeric), round, 2))

p_land <-avg_land_per_hh_reg %>% 
  plot_ly(x=~woreda, 
          y=~avg_land_size_hh, 
          color=,
          colors=colors9,
          text=~avg_land_size_hh,
          textposition="outside",
          hovertext = ~paste("Woreda=", woreda, "<br>", "Avg Land Size=", avg_land_size_hh, "<br>"), 
          hoverinfo = "text") %>% 
  add_bars() %>% 
  layout(title="",
         xaxis = list(title="", categoryorder = "total descending"),
         yaxis = list(title = "Land size"),
         barmode="group")
p_land <- plotly::config(p_land, displayModeBar = FALSE)
p_land
```

### **Knowelage about apeals to KAC**

```{r }
colors9=c('#009FBD','#FF6000', '#FFD93D', '#7AA874')

Appeal<- hh_data %>% 
  
  group_by(woreda, S9_Q2) %>%
  count(name="n_answers") %>%
  group_by(woreda) %>% 
  drop_na() %>% 
  mutate(percent_answers = n_answers / sum(n_answers)) %>% 
  #mutate(across(where(is.numeric), round, 0)) %>% 
  mutate(percent_answers_label = percent(percent_answers, accuracy = 1)) %>%
  
  #filter(S9_Q2=="Yes") %>% 
  
   plot_ly(x=~woreda, 
          y=~n_answers, 
          text=~percent_answers_label,
          textposition="outside",
          colors=colors9,
          color=~S9_Q2,
          hovertext = ~paste("Woreda=", woreda, "<br>", "Percent=", percent_answers_label, "<br>", "n=",n_answers), 
          hoverinfo = "text") %>% 
         
  add_bars() %>% 
  layout(title="",
         xaxis = list(title="", categoryorder = "total descending"),
         yaxis = list(title = "n"),
         barmode="group")

Appeal <- plotly::config(Appeal, displayModeBar = FALSE)
Appeal
```


### **Beneficiary of PSNP Livelihood Support(%)**

```{r }
colors10=c('#009FBD','#FF6000')
lh_suport<-hh_data %>% 
  group_by(woreda, S8_Q1) %>%
  count(name="n_answers") %>%
  group_by(woreda) %>% 
  mutate(percent_answers = (n_answers / sum(n_answers))) %>% 
  mutate(percent_answers_label = percent(percent_answers, accuracy = 1)) %>%
  #mutate(across(where(is.numeric), round, 0)) %>% 
  #filter(S8_Q1=="Yes") %>% 
  
   plot_ly(x=~woreda, 
          y=~n_answers, 
          text=~percent_answers_label,
          textposition="outside",
          color=~S8_Q1,
          colors=colors10,
          hovertext = ~paste("Woreda=", woreda, "<br>", "Percent=", percent_answers_label, "<br>", "n=",n_answers), 
          hoverinfo = "text") %>% 
          layout(text = list(ticksuffix = "%")) %>% 
  add_bars() %>% 
  layout(title="",
         xaxis = list(title=""),
         yaxis = list(title = "n"),
         barmode="group")
lh_suport <- plotly::config(lh_suport, displayModeBar = FALSE)
lh_suport
```

column 
-------------------------------------

### **Last transfer received from**
```{r}

receive_transfer<- hh_data %>% select(S5_Q34) %>% group_by(S5_Q34) %>% mutate(S5_Q34 = str_replace(S5_Q34,"Cash transfer made using the traditional approach of WOFED cashiers", "WOFED cashiers"),S5_Q34 = str_replace(S5_Q34,"Cash transfer made electronically (e-payment)", "e-payment"))  %>%
  summarise(count = n()) %>% drop_na()


colors=c('#7149C6','#89375F','#CE5959')

      
p_receive_transfer <- plot_ly(receive_transfer, labels = ~S5_Q34, values = ~count, type = 'pie', marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))
p_receive_transfer <- p_receive_transfer %>% layout(title = '',showlegend = TRUE,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

p_receive_transfer


```

### **Current mode of transfer**
```{r}
current_transfer <-hh_data %>% select(S5_Q18) %>% group_by(S5_Q18) %>% 
  summarise(count = n()) %>% drop_na() %>% 
  hchart('pie', hcaes(x = S5_Q18, y = count)) %>% 
  hc_tooltip(pointFormat='<b>Proportion: </b> {point.percentage:,.2f}%') %>% 
  hc_title(text = '', style = list(fontSize = '12px', fontWeight = 'bold')) 
current_transfer

```

### **Preference of transfer modality**
```{r}
choice_modality <-hh_data %>% select(S5_Q42) %>% group_by(S5_Q42) %>% 
  summarise(count = n()) %>% drop_na() %>% 
  hchart('pie', hcaes(x = S5_Q42, y = count)) %>% 
  hc_tooltip(pointFormat='<b>Proportion: </b> {point.percentage:,.2f}%') %>% 
  hc_title(text = '', style = list(fontSize = '12px', fontWeight = 'bold')) 
choice_modality
```

